A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-19 colt-21/cvx-flats.tex
Making P-codimension changes in Hari results

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \simplex \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \simplex \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$.
We call a property $\Gamma: \simplex \toto \R$ \emph{discrete} if $\R$ is a finite set.
A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\simplex$.
%, in which case we write $\Gamma:\simplex\to\R$.
When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}.
Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\simplex \toto \R$ if $L$ elicits a property $\Gamma: \simplex \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

@@

An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\raf{Check me!}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\jessie{Aiming for a unified definition here}
\begin{definition}[\jessie{Unified definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

	%recover this later
	\btw{Jessie: Suggest delete}
	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
\end{definition}
\jessie{There's a bit of nuance about $W$ being a matrix vs function}

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
\jessie{Be explicit about corollary; add corollary after Thm 11.}
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem \ref{thm:cvx-flats} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Theorem \ref{thm:cvx-flats} also gives a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$. \jessie{Does AA15 do this?  Seems out of the blue without that context.}
\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.

@@

		\emph{Infinite $\Y$: }	
		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite[Corollary 1]{rockafellar1982interchange}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \cl\{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s. in } p\}$.\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result.}
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.
		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}

@@

\begin{corollary} 
	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

	\jessie{TODO: Pull in consistency}
\end{proof}

@@

\begin{corollary} 
	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
	For all $p \in \relint{\P}$, there is some flat $F$ \jessie{of \Pcodimension at most $d$} such that $p \in F \subseteq \gamma_r$.
	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

	\jessie{TODO: Add in consistency bit}
\end{proof}

\btw{Jessie: Suggest delete - this is the original version}
\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if a convex $L: \reals^d \times \Y \to \reals$ \jessie{in $\L_d$} indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
By restricting slightly to the broad class of minimizable losses $\L$ \jessie{$\L^{fin}$}, we show their bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
(We conjecture that the restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
% \footnote{We conjecture, as an intriguing open problem, that even this restriction can be lifted and the bound of \citet{ramaswamy2016convex} can be entirely recovered via indirect elicitation lower bounds; perhaps by generalizing the definition of indirect elicitation to apply to non-minimizable losses in some way.}
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
\end{definition}

\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$.
It turns out that the subspace of feasible directions is essentially a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
%\raft{Revisit this sentence! \bo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \to \reals^\Y_+$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	First, take $p \in \relint{\simplex}$ for intuition.
	Theorem~\ref{thm:cvx-flats} guarantees the existence of a flat $F$ of dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. \jessie{Need to be careful to relate \Pcodimension to dimension}
	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
	This yields $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

@@

\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
There are some cases where the bound provided by Theorem~\ref{thm:cvx-flats} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For an example of how Theorem~\ref{thm:cvx-flats} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e. a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}. 
When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

However, consider any flat of codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
See Figure~\ref{fig:flats-bound} for intuition.
Therefore, we have no flat of codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.

>>>>

\begin{definition}[Property, elicits]
	A \emph{property} is a set-valued function $\Gamma : \P \to 2^\R \setminus \{\emptyset\}$, which we denote $\Gamma: \P \toto \R$.
	A loss $L : \R \times \Y \to \reals$ \emph{elicits} the property $\Gamma$ if
	\begin{equation}
    \label{eq:elic}    
    \forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R} \exploss{L}{u}{p}~.
	\end{equation}
\end{definition}

The \emph{level set} of $\Gamma$ at value $r\in\R$ is $\Gamma_r := \{p \in \P : r \in \Gamma(p)\}$.
We call a property $\Gamma: \P \toto \R$ \emph{discrete} if $\R$ is a finite set.
A property is \emph{single-valued} if $|\Gamma(p)| = 1$ for all $p\in\P$.
%, in which case we write $\Gamma:\simplex\to\R$.
When $L\in\L$, we use $\Gamma := \prop{L}$ to denote the unique property elicited by $L$ from eq.~\eqref{eq:elic}. \jessie{Small detail: probably want to specify the domain in this notation at least once, since we move away from $\P = \simplex$}
Finally, we typically denote the target property by $\gamma$, and the surrogate by $\Gamma$.

To relate property elicitation to consistency, we need to allow for a link function, which gives rise to the notion of \emph{indirect} elicitation.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \U$ such that for all $u \in \U$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}
% While there are several possible set-valued extensions, Definition~\ref{def:indirectly-elicits} best matches  suited for studying consistency.
% There are a few possible definitions of indirect elicitation, but this is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
% Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and we must do so deterministically.

@@

An important caveat to the above definitions is that, since $\Gamma = \prop{L}$ is nonempty everywhere, we must have $L\in\L$, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in e.g.~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift the minimizable restriction entirely.
\raf{Check me!}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\begin{definition}[\jessie{Updated definition: }Flat]\label{def:flat-general}
	A \emph{flat} $F \subseteq \P$ $\subseteq \reals^n$ is a nonempty set $F = \ker_\P(W) = \{q \in \P : \E_q W = \vec 0\}$ for some $W:\Y \to \reals^d$.
	Furthermore, we define $\codim(F) := \dim(\spn(\P) / \spn(F))$.

	%recover this later
	\btw{Jessie: Suggest delete}
	If $n$ is finite, the codimension of $F$ is given by $\codim(F)=\mathrm{rank}(W)$.
	If $n$ is infinite, consider $\codim(F) = \dim(\{p + F : p \in \P\}) \leq d$.
\end{definition}

We now state our elicitation lower bound, which when combined with Theorem \ref{thm:consistent-implies-indir-elic}, implies consistency bounds.
\jessie{Be explicit about corollary; add corollary after Thm 11.}
A similar result is \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} instead bound the dimension of flats contained in the level sets, an additional power which we leverage in our examples.
Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} also give a lower bound for any given target $\ell$ or $\gamma$, rather than a given surrogate $L$. \jessie{Does AA15 do this?  Seems out of the blue without that context.}
\raf{Cut the last bits here; I bet AA15 thought of their result as being about consistency, though I could be wrong}
% (although an analogous implication of their Theorem 9 may have been known to \citet{agarwal2015consistent}).
% We also note that the lower bound on elicitation complexity in \citet{agarwal2015consistent} is not translated into a lower bound for \emph{consistent} surrogates, which is the main contribution of this work.

@@

		\emph{Infinite $\Y$: }	
		$L \in \L_d$ and convex implies $L$ satisfies the assumptions of~\cite{ioffe1969minimization}, we can interchange subdifferentiation and expectation to observe $\partial \E_p L(u,Y) = \E_p \partial L(u,Y) := \{\int V(y)dp(y) : V \mathrm{measurable}, V(y) \in \partial L(u,y) \textrm{a.s. in } p\}$.
		\jessie{What happens if $\vec 0$ not in the set, but is in the closure}\jessie{Cite~\cite{ioffe1969minimization} instead; they don't use closure and it's the same result. (Instead of ~\cite[Cor 1]{rockafellar1982interchange})}
		We can now take $V_{u,p}$ to be such a $V: \Y \to \reals^d$, which exists as $\vec 0 \in \partial \E_p L(u,Y)$, and therefore, the set is nonempty.

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
	Given target property $\gamma:\P \toto \R$, if there is some $p \in \P$ such that $|\gamma(p)| = 1$ with $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$
	Moreover, if there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

	Now, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
\end{proof}

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
	Given target property $\gamma:\P \toto \reals^d$, where $\P$ is defined over a finite set of outcomes $\Y$.
	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

	As above, if we do not have a flat satisfying the above conditions, then we do not have $\prop{L}$ indirectly eliciting $\gamma$, and in turn do not have a link such that $L$ is consistent with respect to $\gamma$ by Theorem~\ref{thm:consistent-implies-indir-elic}.
\end{proof}

\btw{Jessie: Suggest delete - this is the original version}
\begin{theorem}\label{thm:cvx-flats}
  Let a property $\gamma:\simplex\toto\R$ be given, let $p\in\simplex$ such that either (i) $|\gamma(p)|=1$ or (ii) $\gamma$ is elicitable and $p\in\relint\simplex$, and let $r\in\gamma(p)$.
Then if a convex $L \in \L_d$ indirectly elicits $\gamma$, there is a flat $F$ with $p\in F \cap \simplex \subseteq \gamma_r$ and $\codim(F) \leq d$.
% COmmented 06.03.20
%	If there is a convex surrogate loss $L : \reals^d \times\Y \to \reals$ indirectly eliciting $\gamma$, then for all $p \in \simplex$ and $r \in \R$ such that $r \in \gamma(p)$, there is a flat $F \subseteq \affhull(\simplex)$ of codimension at most $d$ such that $F \cap \simplex \subseteq \gamma_r$ and $p \in F$.
\end{theorem}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss and discrete predictions.
The proof heavily builds around the ``limits of sequences'' in the definition of calibration.
By restricting slightly to the broad class of minimizable losses $\L$, we show their bound follows relatively directly from Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}.
(We conjecture that the minimizability restriction to $\L$ can be lifted; see \S~\ref{sec:conclusions}.)
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at $p \in \C$ is $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
\end{definition}

\citet{ramaswamy2016convex} gives a lower bound on the dimensionality of all calibrated convex surrogates, i.e. $\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1$ for all $p$ and $r \in \gamma(p)$, particularly in the setting where one is given a discrete prediction problem and target loss over finite outcomes.
It turns out that the subspace of feasible directions is essentially a special case of a flat described by Lemma~\ref{thm:convex-flats-inf-dim}.
So, by making a slight restriction to the class of minimizable convex surrogates $\L$, we can derive this lower bound from our general technique in a way that we find shorter and simpler.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
%\raft{Revisit this sentence! \botodo{Visited, had fun, bought the t-shirt.}}\jessiet{lol I don't want to delete this...}

\begin{lemma}\label{lem:Pcodim-codim-finite}
	Suppose we are given a property $\gamma: \P \toto \R$, distribution $p \in \P$ and report $r$ such that $r \in \gamma(p)$, where $\P$ is defined over finite $\Y$.
	For any flat $F$ such that $p \in F \subseteq \gamma_r$ with $\Pcodim(F) \leq d \leq n$, there is a matrix $W \in \reals^{d \times n}$ such that $\{p \in \P : Wp = \vec 0\} = F$ and $\codim(W) = \rank(W) \leq d$.
\end{lemma}
\begin{proof}
	First, let us construct $W$ by taking the function $V$ constructed in the finite $\Y$ case of the proof of Theorem~\ref{thm:convex-flats-inf-dim} (recall $F = \zeros{V}$).
	Construct the $y^{th}$ column of $W$ to be $V(y)$ for each $y \in \Y$.

	We can observe that $Wp = \vec 0 \iff \E_p V = \vec 0$ \jessie{Check} by definition of expectation and its linearity, so $F = \{p \in \P : \E_p V = \vec 0\} = \{p \in \P : Wp = \vec 0\}$. 
	Moreover, by the rank-nullity theorem, we have $\codim(W) = \rank(W) \leq d$.
\end{proof}

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a flat $F$ of \Pcodimension at most $d$ so that $p \in F \subseteq \gamma_r$.
	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \P : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq \{q \in \P : Wq = \vec 0\} - p$.
	Moreover, $\dim(\Sc_{\gamma_r}(p)) \geq n - d - 1$, completing the proof for $p \in \relint{\simplex}$.\jessie{This is a bit convoluted, but I didn't want to override the kernel notation}

@@

There are some cases where the bound provided by Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} is strictly tighter than the bound provided by feasible subspace dimension in Corollary~\ref{cor:fsd-bound}.
For an example of how Corollary~\ref{cor:Pcodim-flat-single-val-prop} applies to a discrete property for which there is no target loss -- a non-elicitable property, i.e. a quadrant not considered by \citet{ramaswamy2018consistent} -- we refer the reader to Appendix~\ref{app:omitted-examples}.

\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\ccdim(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
%% Bo: resolved on Jun 1, afternoon
%\raft{This is a bit of a strawman, since the FSD technique as a whole gives $\geq 1$ here, for e.g.\ $p=(1/4,1/4,1/2)$; let's maybe discuss both $p$'s for both techniques?}\jessiet{Added both distributions.}

However, consider any flat of \jessie{\Pcodimension} codimension $1$ (a line in the two dimensions; a plane in three) containing $p$.
When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
See Figure~\ref{fig:flats-bound} for intuition.
Therefore, we have no flat of \jessie{\Pcodimension} codimension $1$ containing $p$ staying in $\gamma_\bot$, so we obtain better lower bound, $\ccdim(\ell^{abs}) \geq 3 - 0 - 1 = 2$.
